\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Jasper Mayone \\}
\normalsize Fayson, Vermont $\mid$ 802-279-3128 $\mid$ jaspermayone@gmail.com \\
\normalsize linkedin.com/in/jaspermayone $\mid$ github.com/jaspermayone $\mid$ jaspermayone.com/portfolio \\
\hrulefill
\end{center}

\noindent \textbf{\underline{SUMMARY}} \\
Software engineer with extensive hands-on experience in full-stack development, system administration, and technical leadership. Demonstrated success in managing large-scale technical projects and leading development teams. Particularly skilled in creating scalable solutions for community platforms and implementing robust technical infrastructure. \\

\noindent \textbf{\underline{TECHNICAL SKILLS}} \\
\noindent \textbf{Languages \& Frameworks:} JavaScript/TypeScript, Python, Ruby on Rails, Swift, Node.js, Next.js \\
\noindent \textbf{Systems \& Tools:} Docker, PostgreSQL, RSpec, CI/CD, Git, GitHub, Audio/Visual Systems, Network Infrastructure \\
\noindent \textbf{Platforms:} Zoom, Eventbrite, Sched, Point of Sale Systems \\
\noindent \textbf{Other:} Technical Training, Team Leadership, Project Management, Inventory Management \\

\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Wentworth Institute of Technology} \hfill Boston, Massachusetts \\
\textit{Bachelor of Science in Computer Science} \hfill Expected: Fall 2029 \\ \\
\textbf{Harwood Union High School} \hfill Duxbury, Vermont \\
\textit{High School Diploma} \hfill Graduation Date: Jun 2024 \\

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Major League Hacking} \hfill New York, New York \\
\textit{Summer Engineering Intern} \hfill May 2025 - Aug 2025
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Developed and implemented technical integrations between MyMLH identity platform and Discord using Ruby on Rails, enhancing user experience and data synchronization.}
\item {Attended daily standups and bi-weekly sprint planning meetings, collaborating with cross-functional teams to ensure project alignment and timely delivery.}
\item {Contributed to code reviews and pair programming sessions, fostering a collaborative development environment and knowledge sharing.}
\item {Implemented automated testing solutions to improve code quality and reduce regression issues.}
\item {Participated in retrospectives, providing feedback and suggestions for process improvements. \\}
\end{itemize}

\noindent \textbf{The Hack Foundation} \hfill Shelburne, Vermont \\
\textit{Gap Year Software Engineer} \hfill Oct 2023 - Jul 2024
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Led and mentored a cross-functional team of developers across several major software projects.}
\item {Maintained GitHub repositories with 1000+ commits, including implementing CI/CD pipelines.}
\item {Architected and developed custom software solutions handling 10,000+ daily users, including automated moderation tools and community platforms}
\item {Served as lead moderator for 50,000+ member technical community of teens.}
\item {Built and led community management team of 10, with the goal of improving the number of active members. \\}
\end{itemize}

\noindent \textbf{Harwood Union High School} \hfill Duxbury, Vermont \\
\textit{Student Tech Assistant} \hfill Sep 2021 - Jun 2024
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Detected and remediated network security threats and malware incidents across district infrastructure while maintaining network uptime.}
\item {Managed district-wide inventory of 5,000+ devices across 6 schools.}
\item {Assisted technical support team serving students and staff.}
\item {Deployed network infrastructure including cable runs and switches.}
\item {Developed and delivered technical training for 2 Student IT interns.}
\item {Spearheaded software automation projects. \\}
\end{itemize}

\noindent \textbf{Signal Kitchen} \hfill Burlington, Vermont \\
\textit{Bookshop Manager \& Assistant to Events Director} \hfill Feb 2023 - Feb 2024
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Leveraged Eventbrite and Sched platforms to coordinate registration and check-in for thousands of attendees at See Change flagship events.}
\item {Streamlined pre/post event operations through database management and organization.}
\item {Coordination of vendor relationships while managing shipping logistics for event bookstore.}
\item {Developed and maintained inventory management and point of sale system for bookstore.}
\item {Assist guests during event, as well as on-site support for overnight VIP guests.}
\end{itemize}

\end{document}