\documentclass[10pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

% Format section titles
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% Remove page numbers
\pagestyle{empty}

% Customize itemize spacing - use dashes
\setlist[itemize]{label=--, leftmargin=*, nosep, itemsep=1pt, topsep=3pt}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Jasper Mayone}} \\[2pt]
    me@jaspermayone.com | Boston, MA | \href{https://linkedin.com/in/jaspermayone}{linkedin.com/in/jaspermayone}
\end{center}

\vspace{-2pt}

% Education
\section{Education}
\noindent
\textbf{Wentworth Institute of Technology | Boston, MA} \hfill Expected Graduation: 08/2025 \\
Bachelor of Science in Computer Science \\
% Overall GPA 3.0/4.0, Major GPA 3.2/4.0 \\
\textit{Related Courses:} Computer Science II, Computer Organization, Computer Science + Society Studio, Climate Change and the Humanities, Calculus 1

\vspace{2pt}

% Skills
\section{Skills}
\noindent
\textbf{Programming Languages:} Javascript, Typescript, Ruby on Rails, Swift, Node.js, Next.js, SQL \\
\textbf{Software:} Visual Studio Code, Eclipse, Xcode, Adobe Creative Suite, Stripe

\vspace{2pt}

% Projects
\section{Projects}
\noindent
\textbf{Slack Profile CLI | Open Source Tool (Individual)} \hfill 10/2025
\begin{itemize}
    \item Built command-line tool for managing Slack user profiles programmatically using Node.js and Ruby
    \item Published to npm and RubyGems package registries with Homebrew distribution support
    \item Implemented interactive mode with autocomplete and batch operations for workspace administrators
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Obsidian AI Note Tagger | Obsidian Plugin (Individual)} \hfill 03/2025
\begin{itemize}
    \item Developed TypeScript plugin that uses AI to automatically tag notes based on content analysis
    \item Integrated with Obsidian's API to provide seamless note organization for users
    \item Published as open source project with 6+ GitHub stars
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Personal Website | Portfolio \& Blog (Individual)} \hfill 06/2024 -- Present
\begin{itemize}
    \item Built full-stack personal website using Next.js, TypeScript, and Tailwind CSS
    \item Implemented dynamic routing, SEO optimization, and responsive design
    \item Deployed with continuous integration using GitHub Actions
\end{itemize}

% Experience
\section{Experience}
\noindent
\textbf{Major League Hacking | New York, NY | Summer Engineering Intern} \hfill 05/2025 -- 08/2025
\begin{itemize}
    \item Developed and implemented technical integrations between MyMLH identity platform and Discord using Ruby on Rails, enhancing user experience and data synchronization.
    \item Attended daily standups and bi-weekly sprint planning meetings and retrospectives, collaborating with cross-functional teams to ensure project alignment and timely delivery.
    \item Implemented automated testing solutions to improve code quality and reduce regression issues.
    \item Participated in retrospectives, providing feedback and suggestions for process improvements.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{The Hack Foundation | Shelburne, VT | Gap Year / Software Engineer} \hfill 10/2023 -- 07/2024
\begin{itemize}
    \item Led and mentored a cross-functional team of developers across several major software projects.
    \item Designed and developed custom software solutions.
    \item Built and led community management team of 10, with the goal of improving the number of active members.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Signal Kitchen | Burlington, VT | Bookshop Manager \& Assistant to Events Director} \hfill 02/2023 -- 02/2024
\begin{itemize}
    \item Leveraged event platforms to coordinate registration and check-in for thousands of attendees at flagship events.
    \item Streamlined pre/post event operations through database management and organization.
    \item Coordination of vendor relationships while managing shipping logistics for event bookstore.
    \item Developed and maintained inventory management and point of sale system for bookstore.
    \item Assist guests during event, as well as on-site support for overnight VIP guests.
\end{itemize}


% future note - hackwit start 10/2025

% Activities
\section{Activities}
\noindent
\textbf{WITCC (Wentworth's student run coding club) | Treasurer \& Member} \hfill 09/2025 - Present
\begin{itemize}
    \item Managed Club budget
    \item Sat on E-Board which included event/meeting coordination and other leadership tasks
\end{itemize}

\end{document}
